\section*{Abstract}
\label{sec:abstract}


Currently, we live in a world that is highly consumer of digital content and in this sense there is a need on the part of companies to adapt digital marketing techniques. Unlike traditional marketing in which companies reach the public, Inbound marketing is a set of techniques and approaches that make the public reach companies freely. Nowadays nobody wants to be interrupted by advertisements and anyone looking for solutions online has to be convinced very quickly. In other words, it is necessary to provide content that has value for the target audience.

During this internship, a tool that allows companies to create campaigns was developed, following inbound marketing strategies.

10.Quest is an Inbound Marketing platform, which will be developed, marketed and used by 10.digital, which allows you to create and publish different types of campaigns to generate leads, and these campaigns can be personality quizzes, contests and/or trainings. Those leads, whitch in the beginning are only visitors/interested people will become potencial costumers (i. e. at this point they become leads witch are potencial costumers whom we have personal data) by participating in the campaigns and ideally they become constumers/consumers. The data collected by the campaigns, is processed by the system and represented through reports that helps the platform users to generate \textit {leads} and create personality profiles, understand market trends and optimize new other campaigns.



\section*{Keywords}
\label{sec:keywords}

Inbound Maketing, Web Application, Marketing Campaigns, Campaign Optimization, Leads 
